\documentclass[main.tex]{subfiles}
\section{Conclusion}
To make a general conclusion it is again necessary to look back at the stated objectives.
\textbf{Main objective: }
\begin{itemize}
    \item Design a system that recognizes license plates.
\end{itemize}
\textbf{Side Objectives: }
\begin{itemize}
    \item Moving Images
    \item CUDA: parallel processing.
\end{itemize}
The main objective is met.
The system designed and described is capable of distracting a number plate from a picture.
It is possible to identify different kind of number plates and the system is transparent so it easy to implement in a larger or other system.
The results make it clear that the system is not perfect.
There can be made mistakes.
The most mistakes are made when there is a lot more text in the pictures and specifically wen the font size is similar to the license plate.
For the main objective the following conclusion can be made:\\
The objective is met but is not 100\% effective. Therefor this system is good for academic purposes but not ready to be used in the street.
Actual traffic control camera's have a way more complex system en probably determine the license plate in a few ways to be absolutely certain.
Also the fact that the specifics of the license plate have to be in the script rules this out as a real world system.
In a real world system all license plates have to be recognized not knowing which country region or design they have.
To achieve this, it is possible that a complete different approach is necessary.
\par
The side objectives are both not met.
Processing moving images proves to be too complex to do in the span of this course.
Maybe this can be done as a secondary project using the findings I've become.
It is also possible that the clue to find the solution for the trade offs of the main objective can be found in the use of moving images.
The fact why CUDA programming was not an option is already discussed in this report.
An interesting study would be implementing my solution with parallel processing and observe what the time difference would be.
In this way it should become clear in which way a custom designed system with parallel processor is necessary to make a system conforming the needs.
Of course the conclusion of that research can be different when using images or moving images.